---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# projecthelpers

<!-- badges: start -->
[![R-CMD-check](https://github.com/TeroJii/projecthelpers/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/TeroJii/projecthelpers/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of projecthelpers is to provide convenience functions which aim to make common tasks, such as defining the project data folder path, easier.

## Installation

You can install the development version of projecthelpers from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("TeroJii/projecthelpers")
```

## Examples

### Setting the project data folder path

The package provides a function to get the path to the data folder in your project. This is useful when you want to load data files from a specific folder on your computer. You can use a `.env` file with the [{dotenv} package](https://github.com/gaborcsardi/dotenv) to set the path to the project folder, or you can specify the path directly in the function call.

```r
library(projecthelpers))
## basic example code
get_datapath(data_folder = "Data", use_dotenv = TRUE)
```

The structure of the `.env` file should be as follows:

```bash
# example of a OneDrive path
PROJECT_PATH="MyCompany/Project1 - Documents/Development"

```

### Listing files in the project data folder

You can also use the package to list all files in the project data folder. This is useful when you want to see what files are available in the folder.

```r
library(projecthelpers)

my_data <- get_datapath(data_folder = "Data", use_dotenv = TRUE)

list_files(my_data)
```

You can now use the `subset_filetype()` function to filter the files by file type. For example, if you want to list all CSV files in the data folder, you can use the following code:

```{r}
library(projecthelpers)
# example filenames in the data folder
my_files <- c(
  "file1.csv",
  "file2.csv",
  "file3.txt",
  "file4.csv"
)

# List all CSV files in the data folder
subset_filetype(my_files, extension = "csv")
```

